%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\vspace{-0.2cm}
 \cventry
    {Data Engineering Lead} % Job title
    {Debiopharm} % Organization
    {Lausanne, Switzerland} % Location
    {July 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architect \& implement a validated enterprise-data-warehouse solution to collect-harmonize-process clinical data}
        \item {Build an entity-extraction \& search engine to construct knowledge-graphs \& perform trend-monitoring \& analysis}
        \item {Conduct due-diligence of the technical stacks of AI-based startups to aid digital health investment decision}
      \end{cvitems}
    }

	
 \cventry
    {Senior Data Engineer} % Job title
    {SOPHiA Genetics} % Organization
    {Lausanne, Switzerland} % Location
    {April 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scalable infrastructure development for optimal extraction, transformation, \& loading of large-complex datasets}
        \item {Analytical tool development for data-pipelines to provide actionable insights into business performance metrics}
        \item {API \& CLI tools development to expose database functionalities; Formal specification write-ups for requirements}
      \end{cvitems}
    }

  \cventry
    {Software Engineer | Research \& Development Lead} % Job title
    {GenLots} % Organization
    {Lausanne, Switzerland} % Location
    {Sept. 2019 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Implemented \& scaled microservices-based architecture to ingest \& serve client data to our production ML service}
      	\item {Optimized(C/C++ bindings) \& removed bottlenecks in the machine-learning service, shipped end-to-end features}
        \item {Developed reporting \& logging tools to automate client delivery services, Led \& supervised industrial R\&D projects}
      \end{cvitems}
    } 
   

  \cventry
    {Research Scientist} % Job title
    {Distributed Object Programming Lab} % Organization
    {Lausanne, Switzerland} % Location
    {Nov. 2015 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Implemented an infrastructure to load high-frequency streaming public transport ridership data to a relational DB}
      	\item {Implemented a supervised ML-based service to minimize ticket-free riding on Lausanne public transport network}
        \item {Led a large-scale open geospatial data collection campaign; Worked with the team to implement backend system}
      \end{cvitems}
    }


  \cventry
    {Project Intern} % Job title
    {ETH Zürich} % Organization
    {Zürich, Switzerland} % Location
    {Jan. 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Implemented software-defined-radio based platform to generate repeatable \& controllable interference patterns}
        \item {Deployed the platform on open IoT testbeds; Designed tools \& APIs to control \& perform automated benchmarking}
      \end{cvitems}
    }

  \cventry
    {Embedded Systems Engineer} % Job title
    {BOLT IoT} % Organization
    {Goa, India} % Location
    {Aug. 2011 - Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Designed \& optimized PCB layouts of embedded platforms for robotics \& IoT applications; Set-up testing strategies}
        \item {Implemented tools \& applications to benchmark platform performance; Led client support \& troubleshooting teams}
      \end{cvitems}
    }
    
    \vspace{-0.4cm}

\end{cventries}
