%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Skills \& Competencies}

\begin{itemize}[leftmargin=*]

\item {\paragraphstyle{\textbf{software \& design:} Python, Java, Scala and Rust. Skills: object-oriented-programming, test-driven development \& software design patterns}}

\vspace{-0.2cm}

\item {\paragraphstyle{\textbf{database management:} PostgreSQL, MySQL, MongoDB, Cosmos DB, Redis. skills: data modeling, query optimisation, replication \& migration}}

\vspace{-0.2cm}

\item {\paragraphstyle{\textbf{data engineering:} architecting ETL pipelines (Azure Data Factory, Azure Synapse Analytics, Data Build Tool (DBT), Apache Airflow, \& Databricks)}}

\vspace{-0.2cm}

\item {\paragraphstyle{\textbf{infrastructure \& services:} Docker, Kubernetes, Kafka, Azure and AWS. skills: containerisation, orchestration, on-prem monitoring with Zabbix}}

\vspace{-0.2cm}

\item {\paragraphstyle{\textbf{machine learning \& data science:} NumPy, scikit-learn, TensorFlow, PyTorch. skills: data cleaning \& quality patterns, DL-models and validation}}

\vspace{-0.2cm}

\item {\paragraphstyle{\textbf{observability \& monitoring:} Elasticsearch-Kibana-Logstash, Prometheus, Grafana. skills: logging, traceability, alerting and anomaly detection}}

\vspace{-0.2cm}

\item {\paragraphstyle{\textbf{devops \& versioning:} Azure DevOps, GitHub Actions, Terraform and Ansible. skills: release management, pipeline automation (CI/CD) and IaC}}

\vspace{-0.2cm}

\item {\paragraphstyle{\textbf{data visualization:} matplotlib, Tableau, Dash, Power BI, SAS visual analytics. skills: interactive dashboards, data wrangling and transformation}}

\vspace{-0.2cm}

\item {\paragraphstyle{\textbf{security:} Azure DevOps security, Darktrace and Firewall configuration. skills: security policies, application \& infrastructure security procedures}}

\vspace{-0.2cm}

\item {\paragraphstyle{\textbf{LLM (GPT)-based app development:} OpenAI APIs, Vector Databases \& Langchain. skills: fine-tuning \& training techniques, prompt engineering}}

\vspace{-0.2cm}

\item {\paragraphstyle{\textbf{project management:} Atlassian Suite (JIRA, Confluence and Bitbucket). skills: agile methodologies, sprint planning and backlog prioritization}}

\vspace{-0.2cm}

\item {\paragraphstyle{\textbf{languages}: English (fluent), French (working proficiency, B2), German (elementary proficiency, A2), Hindi (Fluent), Marathi and Konkani (Native)}}

\end{itemize}

\vspace{-0.25cm}
